\documentclass{report}

\title{Simulation assignment}
\author{Chiel ten Brinke (3677133) and Mattias Beimers (3672565)}
\date{\vspace{-3ex}}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{float}
\usepackage[margin=1.75in]{geometry}
\usepackage[parfill]{parskip}

\usetikzlibrary{arrows,shapes,decorations.pathmorphing}

\newcommand{\Break}{\State \textbf{break}}
\renewcommand{\qed}{\hfill \ensuremath{\square}}

\newcommand{\calC}{\ensuremath{\mathcal{C}}}
\newcommand{\calCC}{\ensuremath{\mathcal{C'}}}
\newcommand{\reduc}{\ensuremath{\leq_P} }

\begin{document}
\tikzstyle{vertex}=[circle,very thick,draw=black,fill=black!25,minimum size=35pt,inner sep=0pt,align=center,text width=30pt,font=\scriptsize]
\tikzstyle{fakeVertex}=[circle,minimum size=1pt,inner sep=0pt]
\tikzstyle{edge} = [draw,thick,-]
\tikzstyle{arc} = [draw,thick,->]
\tikzstyle{weight} = [font=\scriptsize]

\maketitle
\tableofcontents


\chapter{Problem description}
We present a simulation study for the buffer- and batch-size design of a production line of DVD's.
Moreover, we analyze improvements for the line, by, among others, finding the best buffer- and batch-sizes and alleviating the impact of bottlenecks.

The production process of DVD's consists of the following steps:
\begin{enumerate}[A.]
    \item Injection molding
    \item Dye coating and drying
    \item Sputtering, lacquer coating, drying
    \item Printing and finishing
\end{enumerate}
The machines have limited buffer space, and step C is done with batch processing.
Machines can break down, possibly causing them to be out of production for a while,
and discarding DVD's they were producing. Also some machines need cleaning or replacing of ink.
These problems are solved by repairmen, working in shifts.

Our goal is to optimize the configuration for the batchsize and the buffersizes in terms of performance measures by means of a simulation.
A more detailed description of the simulation that is to be built is found in chapter~\ref{problem_analysis}.

\chapter{Analysis of the problem}
\label{problem_analysis}
Here follows a more detailed description of the production line that is to be simulated.

\section{Machines and buffers}
There are 4 machines of type A, and 2 machines of each of the types B, C and D.
Machine A has unlimited raw material input.
Between every two types of machines there are buffers of a certain size, which can store DVD's until they are fetched by a machine.
There are two buffers between type A and B, each of which can only from a fixed pair of machines of type A, and can provide to a fixed single machine of type B.
There are two buffers between type B and C, each of which consists of a conveyor belt followed by a crate.
These buffers can only receive from a single machine B, but deliver to any of the machines of type C.
The last buffer, between type C and D, can only receive from a fixed machine C, but deliver to any machine of type D.
The current sizes of each buffer is 20 DVD's.
We want to find out if changing this size results in an improvement of the performance measures.

\section{Batches}
Every machine only processes a single DVD at a time, except for machine C, which processes a whole batch at a time.
The current size of the batch is 20 DVD's.
We want to find out if changing this size results in an improvement of the performance measures.

\section{Breakdowns}
As we already have mentioned, some machines may break down.
This is the case for machines of type A and C.
They break according to a given probability distribution, which is treated in chapter~\ref{input_analysis}.
If such a machine is broken, the DVD's that are currently processed are lost (except for machine of type C), and the machine has to be repaired.
During the day, there are 10 repairmen, and an 11th can be called if necessary.
During the night, there are 7 repairmen, and an 8th can be called if necessary.
Each broken machine can be repaired by a single repairman.
Sometimes, a machine of type A needs two repairmen to be repaired.
When a breakdown occurs while no repairmen are available, the machine will be left as broken, until a repairman comes available.

Machines of type B cannot breakdown, but may destroy a DVD by accident.
Machines of type D cannot breakdown either, but sometimes the ink needs to be replaced.
This costs a repairman as well.
However, the DVD's that are currently processed are not lost.


\chapter{Assumptions}
Here we list the most relevant assumptions for our simulation.
\begin{enumerate}
    \item
        Machine A discards any DVD's that is being produced at the event of a breakdown.
    \item
        When machine A breaks, sometimes there are two repairmen needed to repair it.
        We assume that this happens half of the time.
        This way we are not likely to assume too little.
    \item
        Machines C and D are expected to start with cleaning or ink replacing after the (batch of) DVD's is finished.
    \item
        We assume that a repairman finishes repairing the machine before going home.
    \item
        We start the simulation at 6 o'clock in the morning.
    \item
        We assume that calling an extra repairman costs negligible time.
\end{enumerate}


\chapter{The model}
\section{State}
The factory has a set of state variables, and each of the machines also has some state variables of his own.
The state of the factory consists of the current time, whether it is day or night and the number of repairmen available.

Of course, the state also comprises machines, each of these machines have the following state variables:
the status of the machine, this is used to see if the machine is busy producing DVD's, if it is currently not doing anything, or if it's broken or being repaired (possibly with two repairmen).
It also maintains whether or not it has discarded it's latest DVD\@.

Finally, we have buffers, which are just containers of DVD's.
A special case is the conveyor belt, which also maintains whether it halted or not.
All machines and buffers know from whom they receive and to whom they deliver.

\section{Performance measures}
\label{performance_measures}
We measure the total production of DVD's, the average production speed,
and the average throughput.
Apart from that, we measure some more statistics per machine, to look for bottlenecks:
the number of breakdowns, the total amount of DVD's a machine has produced,
the total amount of discarded DVD's and the time the machine is down, busy producing, or idle.

\section{The eventgraph}
This is our event graph.
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[auto,swap]
        % The machine start and finish events
        \node[vertex] (sA) at (-2,0) {MA start};
        \node[vertex] (fA) at (1,0) {MA finish};
        \node[vertex] (sB) at (-2,-2) {MB start};
        \node[vertex] (fB) at (1,-2) {MB finish};
        \node[vertex] (sC) at (-2,-5) {MC start};
        \node[vertex] (fC) at (1,-5) {MC finish};
        \node[vertex] (sD) at (-2,-7) {MD start};
        \node[vertex] (fD) at (1,-7) {MD finish};

        % Buffer events
        \node[vertex] (assembly) at (-0.5,-3.5) {Put in crate};

        % The breakdown events
        \node[fakeVertex] (sos3) at (-5,-2.2) {};
        \node[vertex] (rfA) at (-4,1) {MA finishes repairing};
        \node[vertex] (rsA) at (-4.5,-1.1) {MA starts repairing};
        \node[vertex] (rfC) at (-4,-4.6) {MC finishes cleaning};
        \node[vertex] (rsC) at (-4,-6.6) {MC starts cleaning};
        \node[vertex] (rfD) at (-0.5,-8.5) {MD finishes ink replacing};

        % The start- and end- of simulation events
        \node[fakeVertex] (sos1) at (-2.5,-1) {};
        \node[fakeVertex] (sos2) at (3,-7.5) {};
        \node[vertex] (eos) at (3.5,-6.5) {End of sim};

        % Arcs for machine start and finish events
        %\node[fakeVertex] (radius4) at (-2.0,1.1) {};
        %\node[fakeVertex] (radius5) at (-1.8,0.6) {};
        %\node[fakeVertex] (radius6) at (-2.2,0.6) {};
        %\path[edge,bend left=60,dashed] (radius6) to (radius4);
        %\path[arc,bend left=60,dashed] (radius4) to (radius5);
        \path[arc,bend left=10] (sA) to (fA);
        \path[arc,bend left=10,dashed] (fA) to (sA);
        \path[arc,dashed] (fA) to (sB); % buffer.add_product
        \path[arc,bend left=10] (sB) to (fB);
        \path[arc,bend left=10,dashed] (fB) to (sB);
        \path[arc,bend left=10] (sC) to (fC);
        \path[arc,bend left=10,dashed] (fC) to (sC);
        \path[arc,dashed] (fC) to (sD); % buffer.add_product
        \path[arc,bend left=10] (sD) to (fD);
        \path[arc,bend left=10,dashed] (fD) to (sD);
        %\path[arc] (fD) to (eos);

        % Arcs for buffer events
        \path[arc,dashed] (sB) to (sA); % buffer.remove_product
        \path[arc,dashed] (fB) to (assembly); % buffer.add_product
        \node[fakeVertex] (radius1) at (-0.5,-2.6) {};
        \node[fakeVertex] (radius2) at (-0.4,-2.9) {};
        \node[fakeVertex] (radius3) at (-0.6,-2.9) {};
        \path[edge,bend left=60,dashed] (radius3) to (radius1);
        \path[arc,bend left=60,dashed] (radius1) to (radius2);
        \path[arc,dashed] (assembly) to (sC); % buffer.add_product
        \path[arc,dashed] (sC) to (sB); % buffer.remove_product
        \path[arc,dashed] (sD) to (sC); % buffer.remove_product

        % Arcs for breakdown events
        \path[arc,bend left=15] (rsA) to (rfA);
        \path[arc,bend left=15,dashed] (rfA) to (rsA); % factory.add_repairman
        \path[arc,dashed] (rfA) to (sA);
        \path[arc,dashed] (fC) to (rsC);
        \path[arc] (rsC) to (rfC);
        \path[arc,dashed] (rfC) to (sC);
        %\path[arc,dashed] (rfC) to (sD);
        \path[arc] (fD) to (rfD);
        \path[arc,dashed] (rfD) to (sD);

        % Start of sim arcs
        \path[draw, thick, ->, line join=round, decorate, decoration=
            {zigzag, segment length=8, amplitude=1,post=lineto, post length=2pt
            }]  (sos1) -- (sA);
        \path[draw, thick, ->, line join=round, decorate, decoration=
            {zigzag, segment length=8, amplitude=1,post=lineto, post length=2pt
            }]  (sos2) -- (eos);
        \path[draw, thick, ->, line join=round, decorate, decoration=
            {zigzag, segment length=8, amplitude=1,post=lineto, post length=2pt
            }]  (sos3) -- (rsA);
    \end{tikzpicture}
    \caption{The eventgraph of the simulation.}\label{fig:event-graph}
\end{figure}

\section{The event handlers}
% Updating state - measure performance, schedule new events.
\begin{enumerate}
    % The machine start and finish events
    \item Machine start:
        this is the event where the machine starts producing his DVD (or batch of DVD's).
        It removes a DVD from the previous buffer
        (except for machine A of course, it creates a new DVD),
        it updates its status to busy, and then schedules the machine end event.
        Removing an item from the previous buffer can possibly schedule a machine start event, if it was doing nothing because the buffer was full.
    \item Machine finish:
        this is the event where the machine finishes producing his DVD (or batch of DVD's).
        It sets it's status to idle and adds a product to one of it's receiver buffers (when they are not full etc.).
        Furthermore it updates the total amount of produced DVD's and it schedules a machine start event.
        Adding an item to the buffer can possibly schedule a machine start event if it was idle due to a full buffer.
        For machine B the finish producing can also discard a DVD,
        for machine C and D it can schedule a start repair event.

    % Buffer events
    \item Put in crate:
        this event is fired when a DVD leaves the conveyor belt, and is put in a crate, that is the buffer between machine B and C.
        It adds the DVD to the buffer of course, and schedules the next put in crate event.
        The conveyor belt is modelled as a queue of times between each DVD on the conveyor belt. That way we can effectively get the time of the first DVD that leaves the conveyor belt.
        This event can also possibly schedule a start producing event in case of idle machines due to a full buffer.

    % The breakdown events
    \item Start repairing:
        this is the event that is fired in case of a breakdown, machine cleaning, or ink replacing. The effect in real life is that a machine cannot be used for a while, and is called start repairing for convenience.
        It updates the status of the machine to repairing
        (or repairing double if two repairmen are nescessary).
        If there are no repairmen available it sets the status to broken.
        It also updates the amount of breakdowns, the amount of discarded DVD's (if nescessary) and the amount of available repairmen.
        It schedules the end repair event.
        Note that machine B does not have repair events.

    \item Finish repairing:
        the end repair event is fired when a repairman is done with it's task.
        It sets the machine's status to idle, adds a repairman (or two) to the available repairmen list.
        It schedules a start producing event and for machine A also the new start repair event.

    % EOS
    \item End of simulation:
        this event ends the simulation, it fires either after a specified duration, or when the user stops the simulation manually.

\end{enumerate}


\chapter{Input analysis}
\label{input_analysis}
Some parameters are exact, others comprise a certain degree of randomness.
For the latter ones, we present here how the data collection (i.e.\ generation) is implemented in the simulation.

Some input spaces are given in the form of a theoretical probability distribution.
Others are given in the form of an empirical probability distribution.
For dealing with empirical distributions, we pick a random number from the sorted empirical data, then pick a number between this number and the next number with uniform probability, i.e.\ we interpolate the empirical distribution linearly.
This way we do not have to care about catching the empirical data in a theoretical probability distribution.
In table~\ref{table:input_table} we have listed the kinds of input data we have for the several machine parameters.

\begin{table}[h]
    \begin{tabular}{|p{4cm}|p{4cm}|p{5cm}|}
    \hline
                    & Machine A         & Machine B         \\ \hline
    uptime          & expontial with mean 8 hours &           \\ \hline
    repairtime      & expontial with mean 2 hours &           \\ \hline
    production time & empirical         & empirical         \\ \hline
    DVD discards    &                   & 2\% of the DVD's  \\ \hline
    \end{tabular}
\end{table}

\begin{table}[h]
    \begin{tabular}{|p{4cm}|p{4cm}|p{5cm}|}
    \hline
                & Machine C                     & Machine D \\ \hline
uptime          & 3\% of batches                & \parbox{5cm}{40\%, 40\%, 20\% uniformly after producing resp. $200, 200 \pm 1, 200 \pm 2$ DVD's} \\ \hline
repairtime      & exact 5 minutes                   & normal with mean 15 minutes and standard deviation 1 minute \\ \hline
production time & sum of two exponentials with mean 10 and 7 seconds plus a fixed 3 minutes   & empirical \\ \hline
DVD discards    &                               & \\ \hline
    \end{tabular}
    \caption {Input distributions}
    \label{table:input_table}
\end{table}


%Machine 1:
    %uptime: exp distr 480min
    %repairtime: exp distr 120min
    %production time: empirical distribution
%Machine2:
    %DVD discard: 2\% of the DVD's uniformly
    %production time: empirical distribution
%Machine3:
    %uptime: 3\% of the batches uniformly
    %production time: exp 10sec / DVD + exp 7 sec / DVD + 3min
%Machine4:
    %uptime: resp. 40\%, 40\%, 20\% uniformly after resp. 200, 200±1, 200±2
    %repairtime: normal mean 15min std 1min
    %production time: empirical distribution





\chapter{Experiments}
% TODO:
% - arguments for running time of choice (steady state etc)
% - input analysis
%
\section{Set up}
Our goal is to give insight in possible improvements in the production process of the DVD production line with respect to changes in the buffersizes and the batchsize of the machines.
To do so, we will mainly investigate the performance measures mentioned in section~\ref{performance_measures}, and see wether they can coexist optimally or there is a trade-off involved.
While having the simulation at hand anyway, we can also have a look for possible bottlenecks caused by things other than the configuration of the buffersizes and the batchsize.

We will choose various configurations for the buffersizes and the batchsize, and run the simulation several times for each of the configurations.

For each configuration:
    run simulation and compute performance measures and confidence interval
    conclude which configurations provide significant improvements


As confidence level $1 - \alpha$ we choose the fairly standard value of $0.95$.
Suppose that we run the simulation, for each configuration, $n$ times, resulting in $n$ sample values, for each performance measure, with mean $\bar{x}$ and deviation $s$.

Then $P(-c \leq T \leq c) = 0.95 $ with $T = \frac{\bar{x} - \mu}{s/\sqrt{n}}$ (student t distribution) and $c = \Phi ^{-1} (1 - \frac{\alpha}{2})= 1.96$.
From this it follows that the confidence interval can be computed as
\[ (\bar{x} - \frac{cs}{\sqrt{n}}, \bar{x} + \frac{cs}{\sqrt{n}}) =
(\bar{x} - \frac{1.96s}{\sqrt{n}}, \bar{x} + \frac{1.96s}{\sqrt{n}}). \]


\section{Results}
Running the simulation gave interesting results.
We simulated a week of the production line for various batch and buffer size configurations.
Moreover, we used 100 fixed seeds for each run, to make sure the confidence interval is decent enough.

We list the most relevant results below that are representative enough to illustrate the conclusions we have drawn from all the results. We don't list all the results here for reasons of clarity.

WORST:
configuration: (40, 200, 200, 40)
production results: (27198.555555555555, 526.30217110386502, [25984.900572713002, 28412.210538398107])
throughput results: (1579.2680692241947, 18.061187139128066, [1537.6188969977538, 1620.9172414506356])

configuration: (40, 40, 200, 40)
production results: (27375.444444444445, 592.06041149885834, [26010.150687338519, 28740.738201550372])
throughput results: (1573.040276998177, 22.339821342340983, [1521.524556606832, 1624.555997389522])

configuration: (40, 20, 200, 40)
production results: (27483.777777777777, 466.31944754695127, [26408.44320348803, 28559.112352067525])
throughput results: (1565.622584597756, 18.322759035563173, [1523.3702264965273, 1607.8749426989848])

BEST:
configuration: (20, 20, 40, 200)
production results: (40960.444444444445, 66.365174751168155, [40807.406077046042, 41113.482811842849])
throughput results: (3191.3877651221392, 147.91704351154394, [2850.2904511426077, 3532.4850791016706])

configuration: (20, 40, 40, 200)
production results: (40987.666666666664, 46.591308202281681, [40880.226917295586, 41095.106416037743])
throughput results: (3133.1749403399695, 123.0249144741494, [2849.478978850454, 3416.8709018294849])

configuration: (20, 200, 40, 200)
production results: (40987.666666666664, 46.591308202281681, [40880.226917295586, 41095.106416037743])
throughput results: (3133.1749403399695, 123.0249144741494, [2849.478978850454, 3416.8709018294849])

configuration: (10, 200, 20, 200)
production results: (41069.666666666664, 27.131879567934266, [41007.100440191782, 41132.232893141547])
throughput results: (4282.6478235611057, 365.30674514012816, [3440.2489587123887, 5125.0466884098232])


\chapter{Conclusions}
From the results presented above we can draw several conclusions.
Let us first focus on the most important performance measure, namely the average production speed.

It is striking to see that the buffersize of buffers after machines of type A hardly matters.
The first three results listed as the best results comprise all possible values of this buffersize, while the other parameters are constant.
Nonetheless, they perform all extremely well.
Furthermore, in all other results (including the worst listed above) the buffersizes of concern appeared to occur randomly with respect to the performance.

The second thing to notice is that all best results have 200 as buffersize for the buffer between C and D.

Thirdly, notice that choosing the batchsize maximal does not give better results.
This could explained by the fact that machine D is a bottleneck in the production line.
Even stronger, a larger batchsize appears too worsen the results a lot.
This could be explained by noticing that machines of type C have to wait longer before it can start and thus leaving itself \emph{and} the machines of type D idle.


The performance of the average throughput seems to be more or less inversely proportional to the performance of the average production speed.
This can be clearly seen in the results listed above, but in the other results, this relation is less clear. Since for this reason the two performance measures cannot be optimized at the same time and since the production speed is clearly most important, we would advise to adapt the batch and buffer sizes to optimize the production speed.

In conclusion we can say that the buffersize between A and B can be left with the current size, namely 20, as it will not improve the performance.
Furthermore, the buffersize between C and D should be high (preferably double the batchsize), as that probably will improve the performance.
The batchsize can also be left as it is, for the reasons explained above.

\chapter*{Appendix}

\section*{Minutes of interview with domain expert}

4 machines of type A, 2 machines B, C and D.
One DVD at a time, except C, which processes batches.
Buffers between each two machines in the line.
Two buffers from A to B.
Buffers between B and C are assembly lines with crates at end.
Size of buffers is 20.
Cannot be greater than 200.
Machine A has unlimited input.

Machines can breakdown.
Machine A: avg 480min uptime, exp distribution.
Repairtime: avg 120min, exp distribution.

Machine B:
    DVD is thrown out.
    Happens to 2\% on average.

Machine C:
­ Breaks down.
  Cleaning costs exactly 5 minutes.
  Happens on average on 3\% of all batches.
  Batch is not lost.
  ­ Production time (3 fases):
        Fase 1: avg 10 sec / dvd, exp distribution.
        Fase 2: avg 6 sec / dvd, exp distribution.
        Fase 3: 3 minutes, exact.

Machine D:
­ Ink needs to be replaced.
  On avg 15min, stdev = 1 min.
  Happens after, 40\% 200 DVDs, 40\% 200 $\pm$ 1 DVD, 20\% 200 $\pm$ 2DVDs.

During the day, there are 10 repairmen, and an 11th can be called if necessary.
During the night, there are 7 repairmen, and an 8th can be called if necessary.

\end{document}
